Taking Dyads Seriously

### 2021-02-04 paper/1_intro.tex
small intro edit

The aim of this study is to address how to estimate regression coefficients in a generalized linear model (GLM) context when there are network dependencies in dyadic data. Specifically, we discuss and evaluate how well the Additive and Multiplicative Effects (AME) model can be used to account for the interdependencies underlying the data generating process of dyadic structures \citep{hoff:2005,hoff:2008,minhas:etal:2019}. The AME works by including a set of parameters meant to capture network effects in the conditional mean equation of the GLM.

>>>>

The aim of this study is to address how to estimate regression coefficients in a generalized linear model (GLM) context when there are network dependencies in dyadic data. Specifically, we discuss and evaluate how well the Additive and Multiplicative Effects (AME) model can be used to account for the interdependencies underlying the data generating process of dyadic structures \citep{hoff:2005,hoff:2008,minhas:etal:2019} in International Relations data. The AME works by including a set of parameters meant to capture network effects in the conditional mean equation of the GLM.
